Untitled

### 2023-10-25 code/analysis_Redo.Rmd
Adding rival capacity

df.util <- dfc %>% 
  inner_join(uds.sites.full %>% 
             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year) %>% 
              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Staff, Assets, Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

@@

@@

p2 <- ggarrange(
  event_study(data = df.util, 
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") , 
  event_study(data = df.util, 
  yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") ,
event_study(data = df.util, 
  yname = "Sites.y", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites"), common.legend = TRUE ) 
p2

@@

df.rival <- dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
  bind_rows(dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(!is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
    left_join(df.comp %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense, 
         fs_contributions = as.numeric(fs_contributions), 
         fs_program_service_revenue = as.numeric(fs_program_service_revenue), 
         fs_other = as.numeric(fs_other), 
         fs_miscellaneous = as.numeric(fs_miscellaneous), 
         ngla_sales_revenue = as.numeric(ngla_sales_revenue), 
         ngla_admin_expense = as.numeric(ngla_admin_expense), 
         fringe_rate = as.numeric(fringe_rate)) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100) %>% 
    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.Homeless)

@@

>>>>

df.util <- dfc %>% 
  inner_join(uds.sites.full %>% 
             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year) %>% 
              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Staff, #Assets, 
         Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

@@

for (j in 10:11){

@@

p2 <- ggarrange(
  event_study(data = df.util,
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  filter(abs(term) <= 5) %>%
  filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") + xlab("Year Relative to Competitive Shock") + ylab("Sites"),
  # event_study(data = df.util, 
  # yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  # filter(abs(term) <= 5) %>% 
  # filter(estimator == "Gardner (2021)") %>% 
  # ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  # #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  # theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  # geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") + xlab("Year Relative to Competitive Shock"),
event_study(data = df.util, 
  yname = "Sites.y", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites") + xlab("Year Relative to Competitive Shock"), common.legend = TRUE ) 
p2

@@

df.rival <- dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
  bind_rows(dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(!is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
    left_join(df.comp %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense, 
         fs_contributions = as.numeric(fs_contributions), 
         fs_program_service_revenue = as.numeric(fs_program_service_revenue), 
         fs_other = as.numeric(fs_other), 
         fs_miscellaneous = as.numeric(fs_miscellaneous), 
         ngla_sales_revenue = as.numeric(ngla_sales_revenue), 
         ngla_admin_expense = as.numeric(ngla_admin_expense), 
         fringe_rate = as.numeric(fringe_rate)) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100) %>% 
    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.Homeless, Assets, Staff)

@@

## Rival Capacity
```{r}

df.rival.util <- df.rival %>% 
  inner_join(uds.sites.full %>% 
             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year) %>% 
              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Staff, #Assets, 
         Sites, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
          Pct.MCD:Pct.Homeless)

did.rival.util <- c(0, 0, 0, 0)

for (j in 10:11){

  df.temp <- df.rival.util[,c(1:9, j, 13:ncol(df.rival.util))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.rival.util <- rbind(did.rival.util, outcomes$coeftable)
}

did.rival.util <- did.rival.util[-1,]
rownames(did.rival.util) <- NULL

p1 <- df.rival.util %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Staff:Sites) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Staff:Sites) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.rival.util) %>%

  #       , group =   gsub(x = df.rival.util %>% 
  # select(Complexity:Intensity) %>% 
  # colnames(), pattern = "^[[:alpha:]]+\\.", replacement = "")) %>% 
  # arrange(desc(group)) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Selection" = 7, "UDS Measure Denom" = 6, "Stinting" = 7)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

p2 <- ggarrange(
  event_study(data = df.rival.util, 
  yname = "Staff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Staff") , 
  # event_study(data = df.rival.util, 
  # yname = "Assets", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  # filter(abs(term) <= 5) %>% 
  # filter(estimator == "Gardner (2021)") %>% 
  # ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  # #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  # theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  # geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Assets") ,
event_study(data = df.rival.util, 
  yname = "Sites", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Sites"), common.legend = TRUE ) 
p2

#summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Assets ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Staff ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.rival.util %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Sites ~ Treated*year.rel))$coeff[4,]
